### 2024-06-20 analysis/analysis.qmd

Initial work to build the data parser from the bibTeX files.

@@

- Update 2024-06-19
- TODO: find better way to read in functions

@@

```{r}
# get metaMER df:

meta_df <- get_metaMER_df(path_2_studies = here::here('studies'))

# get included studies

included_studies <- meta_df[which(
  !stringr::str_detect(meta_df$final_notes, '!EXCL!')),] |> 
  dplyr::tibble()

@@

@@

```{r}
#| eval: false
d <- read.csv('data/meta-analysis_data.csv')
```

We need to identify the core metrics:

- _correlation coefficient_ (obtained from $R^2$) for regression studies.

- _Matthew's correlation coefficient_ for classification studies.

- n (we use STIMULUS_N rather than participant n)

- Subsetting base on model and music qualities

## Analyse

@@

```{r}
#| warning: false
#| eval: false
library(dmetar)
library(tidyverse)
library(meta)

# select regression studies

m.cor <- metacor(cor = valence, 
                 n = stimulus_N,
                 studlab = study_id,
                 data = df,
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 method.random.ci = "HK",
                 title = "MER: Regression: Valence: All")

@@

>>>>

@@

- Update 2024-06-19
- [ ] CA TODO: find better way to read in functions

@@

- [ ] CA ToDo: Check the warning reported here

```{r}
# get metaMER df:
meta_df <- get_metaMER_df(path_2_studies = here::here('studies'))

# get included studies
included_studies <- meta_df[which(
  !stringr::str_detect(meta_df$final_notes, '!EXCL!')),] |> 
  dplyr::tibble()

```
### Recoded

@@

Maybe limit the verbosity of `get_study_results` below

@@

## Summarise annotated data

```{r}
#| eval: true
#| output: asis

print(knitr::kable(table(metaMER_results$citekey,metaMER_results$dimension)))
print(knitr::kable(table(metaMER_results$citekey,metaMER_results$model_id)))
print(knitr::kable(table(metaMER_results$citekey,metaMER_results$feature_id)))
print(knitr::kable(table(metaMER_results$citekey,metaMER_results$data_id)))

## Analysis notes

- [ ] Issue 1: We need unique identifiers for each input component (combine: `study` + `model` + `feature` + `data` + `experiment` that would have be unique id)
- [ ] Issue 2: We `stimulus_N`
- [ ] Issue 3: measure vs statistic?
- [ ] Issue 4: We need to classify the modelling techniques into fewer number of techniques
- [ ] Issue 5: We could polish citekey into ref (xu2021us to Xu 2021 et al., ) for nicer plotting output (can be done with `str_replace`)

@@

```{r}
#| warning: false
#| eval: true
library(dmetar)
library(tidyverse)
library(meta)

# select regression studies with r2
tmp <- dplyr::filter(metaMER_results,dimension=="valence" & measure=="r2")
#sqrt(tmp$values) # convert from R^2 to r
tmp$stimulus_n <- 100 # ad-hoc for now

m.cor <- metacor(cor = sqrt(values), 
                 n = stimulus_n,
                 studlab = citekey,
                 data = tmp,
                 fixed = FALSE,
                 random = TRUE,
                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: All")

print(m.cor)
```

## Explore qualities

```{r}
meta <- metagen(values, sqrt(values), 
                data = tmp, 
                studlab = tmp$citekey, 
                comb.fixed = FALSE, 
                method.tau = "PM")
find.outliers(meta)
infan <- InfluenceAnalysis(meta)
print(eggers.test(meta))

@@

## Sub-group analysis (based on model type)

```{r}

meta <- metagen(values, sqrt(values), # Fix the TE.se 
                data = tmp, 
                studlab = tmp$citekey, 
                comb.fixed = FALSE, 
                method.tau = "PM")

subgroup.analysis.mixed.effects(x = meta, 
                                subgroups = tmp$model_id)
```

## Visualise

```{r}
plot(m.cor)
plot(eggers.test(meta))

### 2024-06-20 index.qmd

We define the aims and methods in [preregistration plan](preregistration/preregistration.qmd), which has beeb preregistered at [OSF]().

## Study Search and Selection

@@

## Data Extraction and Coding

@@

The data will be parsed to tabular format using a custom [library_parser.qmd](studies/library_parser.qmd).

## Analysis

@@

## Manuscript

>>>>

We define the aims and methods in [preregistration plan](preregistration/preregistration.qmd), which has beeb preregistered at [https://osf.io/6y3dr/](https://osf.io/6y3dr/).

### Study Search and Selection

@@

### Data Extraction and Coding

@@

The data will be parsed to a tabular format using a custom [library_parser.qmd](studies/library_parser.qmd).

### Analysis

@@

### Manuscript
